Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2020-07-08 analysis/paper/paper.Rmd
Remove brms from library calls

library("bookdown")
library("brms")
library("knitr")
library("ggplot2")
library("ggpubr")
library("grid")
library("gridExtra")
library("flextable")
library("pander")
library("rice.awd.shb")
library("bayestestR")
library("here")

>>>>

library("bookdown")
library("knitr")
library("ggplot2")
library("ggpubr")
library("grid")
library("gridExtra")
library("flextable")
library("pander")
library("rice.awd.shb")
library("bayestestR")
library("here")
